### 2012-03-24 doc/theses/mikula/experiments.tex
Master thesis: In progress.

\chapter{Experiments}
In this chapter we describe how we performed experiments with the implementation and what problems we encountered.

@@

\begin{table}
\label{TAB_inferred_keys_3}
\caption{Key statements inferred from the extended test data using the modified JP3 statements.}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/people/person, \{@id\})} & 1.0 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{itemref/@item\})} & -0.666 \\ \hline
\end{tabular}
\end{table}

>>>>

\chapter{Experiments} \label{CHAPTER_experiments}
In this chapter we describe how we performed experiments with the implementation and what problems we faced.

@@

\begin{table}
\label{TAB_inferred_keys_3}
\caption{Key statements inferred from the extended test data using the modified JP3 statements.}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/people/person, \{@id\})} & 1.0 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{itemref/@item\})} & -0.333 \\ \hline
\end{tabular}
\end{table}

\todo[inline]{Pripojit vysledne XSD? Je dost velke. Alebo aspon relevantnu cast?}

### 2012-03-24 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

\todo[inline]{Hodil by se příklad stromu - jeslti nebude dál.}

@@

\todo[inline]{priklad stromu}

@@

A syntax tree constructed from sample query in Listing \ref{listing_testing_query_18} is shown in Figure \ref{FIG_syntax_tree_1}.

@@

Figure \ref{FIG_syntax_tree_2} shows the syntax tree of the query in Listing \ref{listing_testing_query_8} (subtree of ConstructorNode is omitted because of lack of space). In this tree, the algorithm founds one occurrence of the join pattern 3. The two for clauses and one where clause which form the occurrence are shown in the red boxes.

>>>>

@@

@@

A syntax tree constructed from sample query in Listing \ref{listing_test_query_18} is shown in Figure \ref{FIG_syntax_tree_1}.

@@

Figure \ref{FIG_syntax_tree_2} shows the syntax tree of the query in Listing \ref{listing_test_query_8} (subtree of ConstructorNode is omitted because of lack of space). In this tree, the algorithm founds one occurrence of the join pattern 3. The two for clauses and one where clause which form the occurrence are shown in the red boxes.
